Models of lens candidates from Space Warps CFHTLS

### 2017-02-28 parts/stelmass.tex
last typo

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}.

>>>>

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.
